Rank Product Tests

### 2021-07-27 R/rank_product_md.Rmd
added 2019 world championships

## Finals Data
load("rp_data.rdata")
```

@@

  return(output)
}
```

```{r}
compare_rp <- function(rp_real, rp_perm) {
  # count how many of the permuted rank-products are smaller than the real rank-product
  sum(rp_real >= rp_perm) %>%
  return()
}

nsim <- 1000
nqual <- nrow(m_qual_rp)
rp_sims <- replicate(nsim, assign_ranks(nqual))
df <- data.frame(first = rep(NA, nqual)
                 , last = rep(NA, nqual)
                 , speed = rep(NA, nqual)
                 , bould = rep(NA, nqual)
                 , lead = rep(NA, nqual)
                 , total = rep(NA, nqual)
                 , count_above = rep(NA, nqual)
                 , E = rep(NA, nqual)
                 , q = rep(NA, nqual)
                 )

@@

>>>>

## Finals Data
load("rp_data.rdata")
load(file = "world_2019_data.rdata")

set.seed(80085)
```

@@

  return(output)
}

compare_rp <- function(rp_real, rp_perm) {
  # count how many of the permuted rank-products are smaller than the real rank-product
  sum(rp_real >= rp_perm) %>%
  return()
}
```

```{r, echo = FALSE}
nsim <- 1000
nqual <- nrow(m_qual_rp)
rp_sims <- replicate(nsim, assign_ranks(nqual))
```

# 2018 Youth Olympics

## Men's qualifiers
```{r, echo = FALSE}
df <- data.frame(first = rep(NA, nqual)
                 , last = rep(NA, nqual)
                 , speed = rep(NA, nqual)
                 , bould = rep(NA, nqual)
                 , lead = rep(NA, nqual)
                 , total = rep(NA, nqual)
                 , count_above = rep(NA, nqual)
                 , E = rep(NA, nqual)
                 , q = rep(NA, nqual)
                 )

@@

## Women's qualifiers
```{r, echo =  FALSE}
df_f <- data.frame(first = rep(NA, nqual)
                 , last = rep(NA, nqual)
                 , speed = rep(NA, nqual)
                 , bould = rep(NA, nqual)
                 , lead = rep(NA, nqual)
                 , total = rep(NA, nqual)
                 , count_above = rep(NA, nqual)
                 , E = rep(NA, nqual)
                 , q = rep(NA, nqual)
                 )

for (i in 1:nqual) {
  t <- f_qual_rp$total[i]                                            # experimental/real score
  #cat(m_qual_rp$first[i], m_qual_rp$last[i], " ", t, "\n")
  s <-  compare_rp(t, rp_sims) %>% sum()                             # count which simulated rp values <= real rp
  e <- s/nsim                                                        # avg expected value
  q <- e/i                                                           # q value (false discovery rate)
  #print(q)
  df_f[i,] <- c(f_qual_rp$first[i]
              , f_qual_rp$last[i]
              , f_qual_rp$speed[i]
              , f_qual_rp$bould[i]
              , f_qual_rp$lead[i]
              , f_qual_rp$total[i]
              , s
              , e
              , q
              )
}

df_f %>% knitr::kable()
```

# 2019 World Championships

```{r}
nqual <- 20
rp_sims <- replicate(nsim, assign_ranks(nqual))
```

## Men's Championships
```{r, echo = FALSE}
df <- data.frame(name = rep(NA, nqual)
                 , speed = rep(NA, nqual)
                 , bould = rep(NA, nqual)
                 , lead = rep(NA, nqual)
                 , total = rep(NA, nqual)
                 , count_above = rep(NA, nqual)
                 , E = rep(NA, nqual)
                 , q = rep(NA, nqual)
                 )

for (i in 1:nqual) {
  t <- world_2019_m_qual$total[i]                                            # experimental/real score
  #cat(m_qual_rp$first[i], m_qual_rp$last[i], " ", t, "\n")
  s <-  compare_rp(t, rp_sims) %>% sum()                             # count which simulated rp values <= real rp
  e <- s/nsim                                                        # avg expected value
  q <- e/i                                                           # q value (false discovery rate)
  #print(q)
  df[i,] <- c(world_2019_m_qual$name[i]
              , world_2019_m_qual$speed[i]
              , world_2019_m_qual$bould[i]
              , world_2019_m_qual$lead[i]
              , world_2019_m_qual$total[i]
              , s
              , e
              , q
              )
}

## Women's Championships
```{r, echo = FALSE}
df <- data.frame(name = rep(NA, nqual)
                 , speed = rep(NA, nqual)
                 , bould = rep(NA, nqual)
                 , lead = rep(NA, nqual)
                 , total = rep(NA, nqual)
                 , count_above = rep(NA, nqual)
                 , E = rep(NA, nqual)
                 , q = rep(NA, nqual)
                 )

for (i in 1:nqual) {
  t <- world_2019_w_qual$total[i]                                            # experimental/real score
  #cat(m_qual_rp$first[i], m_qual_rp$last[i], " ", t, "\n")
  s <-  compare_rp(t, rp_sims) %>% sum()                             # count which simulated rp values <= real rp
  e <- s/nsim                                                        # avg expected value
  q <- e/i                                                           # q value (false discovery rate)
  #print(q)
  df[i,] <- c(world_2019_w_qual$name[i]
              , world_2019_w_qual$speed[i]
              , world_2019_w_qual$bould[i]
              , world_2019_w_qual$lead[i]
              , world_2019_w_qual$total[i]
              , s
              , e
              , q
              )
}
